Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-03-07 paper/method.tex
Replace merge error image and add timing table.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/merge_error_v4.pdf}
\caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
\label{fig:merge_error}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/merge_error_v6.pdf}
\caption{Merge error detection: Potential borders are generated on inverted images by randomly placing watershed seeds (green) on the boundary of a dilated segment. The best ranked seeds and border (both in red) result in the shown error correction.}
%Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
\label{fig:merge_error}
\end{figure}

### 2017-03-07 paper/results.tex
Replace merge error image and add timing table.

\begin{table}[t]
\caption{Classifier comparison on an unbalanced test set of the L.~Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
 & Precision & Recall & F1 score & Test \# \\ 
\midrule
\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
\bottomrule
\end{tabular} 
}
\label{tab:prcyl}
\end{table}

@@

\begin{table}[t]
\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
& Precision & Recall & F1 score & Test \# \\ 
\midrule
\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
Split error & 0.54 & 0.95 & 0.69 & 332 \\ 
\bottomrule
\end{tabular} 
}
\label{tab:prac4}
\end{table}

@@

\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to $0.469$ ($SD=0.87$). On average, users viewed $423.4$ corrections and accepted $45.8$, with an average time of $4.9$ seconds per correction. Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$). Here, users viewed on average $353.4$ corrections and accepted $106.9$, with an average correction time of $6.2$ seconds. While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it. In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo (median VI $0.535$, $SD=0.055$). The slope of VI score per correction (Fig.~\ref{fig:ac4trails}) shows that guided proofreading enables improvements with fewer corrections than the other tools. Interestingly, novice performance decreases after approximately $300$ corrections. There are two explanations for this: user fatigue, and increasing uncertainty during error suggestion from the classifier. %Regarding fatigue, we suggest that future experiments include short breaks after every ten minutes.

>>>>

\begin{table}[t]
\caption{Classifier comparison on an unbalanced test set of the L.~Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
 & Precision & Recall & F1 score & Test \# \\ 
\midrule
\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
~~Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
~~Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
~~Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
~~Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
\bottomrule
\end{tabular} 
}
\label{tab:prcyl}
\end{table}

@@

\begin{table}[t]
\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
& Precision & Recall & F1 score & Test \# \\ 
\midrule
\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
~~Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
~~Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
~~Correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
~~Split error & 0.54 & 0.95 & 0.69 & 332 \\ 
\bottomrule
\end{tabular} 
}
\label{tab:prac4}
\end{table}

@@

\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to $0.469$ ($SD=0.87$). On average, users viewed $423.4$ corrections and accepted $45.8$.
%, with an average time of $4.9$ seconds per correction. 
Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$). Here, users viewed on average $353.4$ corrections and accepted $106.9$.
%, with an average correction time of $6.2$ seconds. 
While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it. In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo (median VI $0.535$, $SD=0.055$). The slope of VI score per correction (Fig.~\ref{fig:ac4trails}) and average timings (Tab.~\ref{tab:correctiontimes}) show that guided proofreading enables improvements with fewer corrections than the other tools. Interestingly, novice performance decreases after approximately $300$ corrections. There are two explanations for this: user fatigue, and increasing uncertainty during error suggestion from the classifier. %Regarding fatigue, we suggest that future experiments include short breaks after every ten minutes.

\begin{table}[h]
\caption{Average proofreading speed for users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP). For comparable correction time, our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
Approach & \makecell{Time Per Correction (s)} & \makecell{VI Reduction Per Minute} \\
\midrule
\emph{Dojo} & 30.5 & -0.002 \\
%\emph{Dojo Expert?} & xxx & xxx \\
\emph{FP} & 4.9 & 0.00023 \\
\emph{GP} & 6.2 & 0.00173 \\
\bottomrule
\end{tabular} 
}
\label{tab:correctiontimes}
\end{table}
